**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-05-23 doc/adaAbstract.Rmd
plots for ada poster

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(ACR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine",
               line = TRUE)

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFR_status, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot2("eGFR_status", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine")

@@

ds %>% 
  dplyr::filter(!(eGFR_status == "Moderate")) %>% 
  dplyr::filter(eGFR < 150) %>% 
  dplyr::select(eGFR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine") +
  ggplot2::geom_smooth(method = lm, colour = "grey50")

>>>>

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_poster("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  scatter_plot_poster("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFRStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_poster("eGFRStatus", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine")

@@

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  scatter_plot_poster("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine")
